\bf An HMM-based part-of-speech tagger for Turkish

### 2015-12-04 paper/paper.tex
Update paper

\documentclass{article}
\usepackage{natbib}
\usepackage{hyperref}

@@

\title{\bf An HMM-based part-of-speech tagger for Turkish}
\author{Ayberk Tosun\\\texttt{tosun2@illinois.edu}}
\date{}

@@

>>>>

\documentclass{article}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{hyperref}

@@

\title{\bf An HMM-based part-of-speech tagger for Turkish}
\author{Ayberk Tosun}
\date{}

@@

\section{Results}

The POS tagger I've built as proposed can successfully tag words with a
reasonable accuracy.

\subsection{Limitations}
There is a fundamental limitation to the POS tagger I built: Turkish morphology
is essential to the overall expressivity of the Turkish language. In English we
entertain the notion of ``syntactic correctness'', which we define as words of a
sentence having some sort of correct order. A speaker of English that has
synactic competence in the language \citep{bachman1990} may know that a sentence
is well-formed, relying on his knowledge of syntactic rules. However, for
\textit{words}, knowledge of morphological rules is not adequate to conclude
that a word is valid; they have to rely on their lexical knowledge to verify
that the morphological form they derived/inflected is a valid one. Consider the
word ``satisfiableness'' which is not a valid word, derived with valid suffixes.
The correct form of this concept is ``satisfiability''. In Turkish, the concept
of word validness is a lot like syntactic correctness; the speaker may rely
their knowledge of morphological rules to \textit{generate} new words. In fact
Turkish has \textbf{recursive} morphology \citep{kabak2001} so a word can be
inflected/derived in into infinitely many different ways. This is why
computational processing of Turkish can never fully escape its morphology.

\section{Conclusion}

% Delete this todo
\todo[inline]{Write a concluding summary. Also indicate what future work may be warranted. This section should be at least half a page in length.}
